Estimation of the road traffic sound levels in urban areas based on non-negative matrix factorization techniques

### 2018-02-07 paper/gloaguenNmfTraffic.tex
Minor corrections and dist-12_12 reframed

\begin{equation}
\tilde{L}_{p,traffic} = 20\log_{10}\left(\frac{p_{rms}}{p_0}\right)
\end{equation}

where $p_{rms}$ is the effective pressure deducted from the remaining spectrogram ($\mathbf{V}_{f_c}$ or $\left[\mathbf{WH} \right]_{traffic}$) and $p_0$ is the reference sound pressure, $p_0 = 2 \times 10^{-5} Pa$.  For each setting of experimental factors, $M$ values of $\tilde{L}_{p,traffic}$, corresponding to the $M$ scenes, are then obtained and are compared to the $M$ exact sound level, $L_{p,traffic}$.

@@

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
      	\includegraphics[width=\linewidth]{figures/semi-sup_bar.pdf}
        \caption{$MAE$ error for each $TIR$ and sub-class with Sem-NMF and $\beta$ = 2}
                \label{fig:TIR_class_semi}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/TI_bar}
        \caption{$MAE$ error for each $TIR$ and sub-class with TI-NMF, $\beta$ = 1 and $t$ = 0.42}
        \label{fig:TIR_class_TI}
    \end{subfigure}
    \caption{$MAE$ error for each sub-class and each $TIR$ according to the the best results with the filter (\subref{fig:TIR_class_filter}) and each method (Sup-NMF (\subref{fig:TIR_class_sup}), Sem-NMF (\subref{fig:TIR_class_semi}) and TI-NMF (\subref{fig:TIR_class_TI}))}
    \label{fig:TIR_bar}
\end{figure*}

@@

However, the relatively high degrees of freedom of Sem-NMF are restrictive for high $TIR$ as the errors exceed 2 dB for all sub-classes and increase with $TIR$ = 6 dB and 12 dB. In order to reduce $D(\mathbf{V} \vert \vert \mathbf{WH}$), without constraint, Sem-NMF is free to include traffic components in $\mathbf{W_r}$. Consequently, this behavior decreases the quality of the reconstruction of the traffic component. In Figure \ref{fig:Y_alert_12} for $TIR=12$ dB, the high frequency components of the alert sounds are lower for the benefit of low frequency content. Consequently, the traffic sound level estimation is then underestimated as in Figure \ref{fig:lp_alert_12}. \\

>>>>

\begin{equation}
\tilde{L}_{p,traffic} = 20 \times \log_{10}\left(\frac{p_{rms}}{p_0}\right)
\end{equation}

where $p_{rms}$ is the effective pressure deducted from the estimated traffic spectrogram $\mathbf{\tilde{V}}_{traffic}$ and $p_0$ is the reference sound pressure, $p_0 = 2 \times 10^{-5} Pa$.  For each setting of experimental factors, $M$ values of $\tilde{L}_{p,traffic}$, corresponding to the $M$ scenes, are then obtained and are compared to the $M$ exact sound level, $L_{p,traffic}$.

@@

    \begin{subfigure}[t]{0.45\textwidth}
        \centering
      	\includegraphics[width=\linewidth]{figures/semi-sup_bar.pdf}
        \caption{$MAE$ error for each $TIR$ and sub-class with Sem-NMF and $\beta$ = 2}
                \label{fig:TIR_class_semi}
    \end{subfigure}%
    \hfill
    \begin{subfigure}[t]{0.45\textwidth}
        \centering
        \includegraphics[width=\linewidth]{figures/TI_bar}
        \caption{$MAE$ error for each $TIR$ and sub-class with TI-NMF, $\beta$ = 1 and $t$ = 0.42}
        \label{fig:TIR_class_TI}
    \end{subfigure}
    \caption{$MAE$ (dB) error for each sub-class and each $TIR$ according to the the best results with the filter (\subref{fig:TIR_class_filter}) and each method (Sup-NMF (\subref{fig:TIR_class_sup}), Sem-NMF (\subref{fig:TIR_class_semi}) and TI-NMF (\subref{fig:TIR_class_TI}))}
    \label{fig:TIR_bar}
\end{figure*}

@@

However, the relatively high degrees of freedom of Sem-NMF are restrictive for high $TIR$ as the errors exceed 2 dB for all sub-classes and increase with $TIR \in \lbrace$6, 12$\rbrace$ dB. In order to reduce $D(\mathbf{V} \vert \vert \mathbf{WH}$), without constraint, Sem-NMF is free to include traffic components in $\mathbf{W_r}$. Consequently, this behavior decreases the quality of the reconstruction of the traffic component. In Figure \ref{fig:Y_alert_12} for $TIR=12$ dB, the high frequency components of the alert sounds are lower for the benefit of low frequency content. Consequently, the traffic sound level estimation is then underestimated as in Figure \ref{fig:lp_alert_12}. \\
